%April 23rd, 2019

\ifplastex
\subsubsection{Usage Of Content}
\label{sec:usage-content}
\else
  \ifstandalone
  \subsubsection{Usage Of Content}
  \label{sec:usage-content}
  \else
  \section{Usage Of Content}
  \label{sec:usage-content}
  \fi
\fi

 THE UML-B PROJECT MAKES AVAILABLE SOFTWARE, DOCUMENTATION, INFORMATION AND/OR OTHER MATERIALS FOR OPEN SOURCE PROJECTS (COLLECTIVELY "CONTENT"). USE OF THE CONTENT IS GOVERNED BY THE TERMS AND CONDITIONS OF THIS AGREEMENT AND/OR THE TERMS AND CONDITIONS OF LICENSE AGREEMENTS OR NOTICES INDICATED OR REFERENCED BELOW. BY USING THE CONTENT, YOU AGREE THAT YOUR USE OF THE CONTENT IS GOVERNED BY THIS AGREEMENT AND/OR THE TERMS AND CONDITIONS OF ANY APPLICABLE LICENSE AGREEMENTS OR NOTICES INDICATED OR REFERENCED BELOW. IF YOU DO NOT AGREE TO THE TERMS AND CONDITIONS OF THIS AGREEMENT AND THE TERMS AND CONDITIONS OF ANY APPLICABLE LICENSE AGREEMENTS OR NOTICES INDICATED OR REFERENCED BELOW, THEN YOU MAY NOT USE THE CONTENT.

\ifplastex
\subsubsection{Applicable Licences}
\label{sec:umlb-applicable-licences}
\else
  \ifstandalone
  \subsubsection{Applicable Licences}
  \label{sec:umlb-applicable-licences}
  \else
  \section{Applicable Licences}
  \label{sec:umlb-applicable-licences}
  \fi
\fi
 
Unless otherwise indicated, all Content made available by the UML-B project is provided to you under the terms and conditions of one of
the following licences.

\begin{itemize}
\item \emph{Eclipse Public License Version 1.0} (EPL) (available at 
   \url{http://www.eclipse.org/legal/epl-v10.html})
\end{itemize}

Content includes, but is not limited to, source code, object code, documentation and other files maintained in the UML-B repository (``Repository'').

The terms and conditions governing Features and Included Features should be contained in files named ``licence.html'' (``FeatureLicences'').  
Feature Licences may be located in any directory of a Download or Module including, but not limited to the following locations:

\begin{itemize}
\item Feature directories

\item Shared-licence feature \texttt{org.rodinp.licence}
\end{itemize}

Note: if a Feature made available by the UML-B Project is
installed using the Eclipse Update Manager, you must agree to a
licence (``Feature Update Licence'') during the installation process.
If the Feature contains Included Features, the Feature Update
Licence should either provide you with the terms and conditions
governing the Included Features or inform you where you can locate
them.  Feature Update Licences may be found in the ``licence''
property of files named ``feature.properties'' found within a
Feature.  Such Feature Licences, and Feature Update
Licences contain the terms and conditions (or references to such
terms and conditions) that govern your use of the associated
Content in that directory.

THE FEATURE LICENCES, AND FEATURE UPDATE LICENCES MAY REFER
TO THE EPL OR OTHER LICENCE AGREEMENTS, NOTICES OR TERMS AND
CONDITIONS.

IT IS YOUR OBLIGATION TO READ AND ACCEPT ALL SUCH TERMS AND
CONDITIONS PRIOR TO USE OF THE CONTENT.  If no Feature
Licence, or Feature Update Licence is provided, please contact the
UML-B Project to determine what terms and conditions govern
that particular Content.
\begin{quote}
  \footnotesize

  \begin{itemize}
  \item  Java and all Java-based trademarks are trademarks of Sun
    Microsystems, Inc. in the United States, other countries, or
    both.
  \end{itemize}
\end{quote}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "user_manual"
%%% End:
